%\VignetteIndexEntry{A Tutorial for CAXA}
\documentclass{article}

\usepackage{Sweave}
\begin{document}

%---------------------------------------------------------------------------------------
\title{A Tutorial for the package CAXA (conspecific attraction experiment analysis)}
%---------------------------------------------------------------------------------------
\author{Sean E. MacDonald}
%\date{December 12th, 2017}

\input{CAXA-concordance}
\maketitle
%---------------------------------------------------------------------------------------
\section{Introduction}
%---------------------------------------------------------------------------------------
The package contains three functions that help clean and analyze data. The Remove.WRSH.ZEDO function removes experiments containing trials of the track species White-rumped shama (WRSH) and Zebra dove (ZEDO) due to low sampling effort. The Keep.15.Tracks function keeps experiments containing trials equal to 15 minutes in order to standardize methodology and low sampling efforts with track lengths not equal to 15 minutes. Lastly, the GLMM.Bin function applys a generalized linear mixed model with a binary distribution to the data in order to see what bird species significantly respond to track species.

The dataset used in this package is a series of 80 experiments with control and treatment periods. Control periods did not include a speaker. During treatment periods bird species' tracks were broadcasted in various orders and lengths (min). Whether or not the experiment was conducted during the bird's breeding season (0 = no, 1 = yes), on a native plant species (0 = no, 1 = yes), and the behavioral response of fruit-eating birds (0 = no response, 1 = attracted) are included. Japanese white-eye (jawe), Red-billed leiothrix (rble), Red-vented bulbul (rvbu), Red-whiskered bulbul (rwbu), and all non-fruit eating species (other). The data was collected on the Island of Oahu, Hawaii, USA from 06/2016 - 07/2017. Sampling took place across 26 native and exotic plant species. Bird breeding season ranges from approximately March - August. 
%---------------------------------------------------------------------------------------
\section{Example}
%---------------------------------------------------------------------------------------
\begin{Schunk}
\begin{Sinput}
> ## Load the required packages and dataset
> library(CAXA)